On the presentation of orthogonal groups over polynomial rings

### 2019-05-03 dl-paper.tex
Minor

\begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] \end{df}
Right from the definition of $S_\alpha(a, -)$ it is easy to verify that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
\[ S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\]

@@

\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P_\beta(0)$. \end{lemma}
\begin{proof}
It suffices to verify the assertion for the generators $z_\gamma(Xf, g)$, $\gamma \in \Phi$.
By our assumption $(\alpha, \beta) \geq 0$. 
\end{proof}

@@

\begin{comment}
($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & -bX^{-1} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 & 0 & * \\
 0 & 1 & * \\
 mX & m'X & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & -bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - mb)^{-1} 
 \end{array}\right) = S_\beta(-b, g^+).
\end{multline}
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 -a & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
\end{multline}
\begin{multline}
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 (1  - bm)^{-1} & 0 & 0 \\
 0 & 1 & 0 \\
 0 & 0 & 1 - bm 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 + abm' & 0 & 0 \\
 0 & (1 + abm')^{-1} & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 a(1 + abm') & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = \\
 = 
 \left(\begin{array}{ccc} 
 1 & - \frac{bm'}{1 + abm'} & * \\
 0 & 1 & * \\
 \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
 \end{array}\right)
\end{multline}
\end{comment}

>>>>

\begin{df} Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ g \in P_\alpha(m).\] \end{df}
It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ holds
\[ S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\frac{a}{1+am}, g_2\right).\]

@@

Our next goal is to determine what happens with the generators of $K(A[X], M[X])$ under the map $S_\alpha(a, -)$.
At first we could look at what happens with $K(A[X], M[X]) \cap P_\alpha(0)$ under $S_\alpha(a, -)$.
We notice the following elements:
\begin{itemize}
 \item $x_\alpha(c)$, $c \in A$;
 \item $x_{\alpha+\beta}(d)$, $\alpha+\beta \in \Phi$
\end{itemize}

\[ x_\alpha(c), , x_{\alpha-\beta}(d) \]

\begin{comment}
\begin{lemma} If $\alpha - \beta \in \Phi$ then for all $g \in \St(\Phi, R[X], XM[X])$ holds $S_\alpha(a, g) \in P_\beta(0)$. \end{lemma}
\begin{proof}
It suffices to verify the assertion for the generators $z_\gamma(Xf, g)$, $\gamma \in \Phi$.
By our assumption $(\alpha, \beta) \geq 0$. 
\end{proof}
\end{comment}

@@

($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & -bX^{-1} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 & 0 & * \\
 0 & 1 & * \\
 mX & m'X & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & -bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - mb)^{-1} 
 \end{array}\right) = S_\beta(-b, g^+).
\end{multline}
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 -a & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
\end{multline}
\begin{multline}
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 (1  - bm)^{-1} & 0 & 0 \\
 0 & 1 & 0 \\
 0 & 0 & 1 - bm 
 \end{array}\right) \cdot \\ \cdot
\left(\begin{array}{ccc} 
 1 + abm' & 0 & 0 \\
 0 & (1 + abm')^{-1} & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 a(1 + abm') & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = \\
 = 
 \left(\begin{array}{ccc} 
 1 & - \frac{bm'}{1 + abm'} & * \\
 0 & 1 & * \\
 \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
 \end{array}\right)
\end{multline}
